### 2020-01-30 Article.tex
A zgz

The analyticity of these asymptotic probabilities with respect to 
the parameter $\beta$ imply that FO properties cannot "capture" sudden
changes that occur in the random graph $\mathrm{G}(n,\beta/n)$
as $\beta$ changes. Given $p(n)$ a probability, $P$ a property of graphs,
and $Q$ a sufficient condition for $P$ - i.e., a property that 
implies $P$ -, we say that $Q$ explains $P$ if $\mathrm{G}(n,p(n))$ satisfies 
the converse implication $P \implies Q$ asymptotically almost surely
(a.a.s.). A notable example of this phenomenon happens in the range 
$p(n)= \log(n)/n + \beta/n$ with $\beta$ constant. Erd\"os and R\`enyi
\cite{erdHos1960evolution} 
showed that for probabilities of this form $\mathrm{G}(n,p(n))$ 
a.a.s. is disconnected only if it contains an isolated vertex. 
An observation by Albert Atserias is the following:

@@

The main theorem of this section is the following

@@

\begin{theorem}
	Let $r\in \N$. Then a.a.s $G_n$ is $r$-simple. 
\end{theorem}
\begin{proof}
	The first moment method alone is not sufficient
	to prove our claim because the amount of dense 
	hypergraphs	$H$ such that $diam(H)\leq r$ is not finite
	in general. Thus, we need to prove that it suffices to
	prohibit a finite amount of dense sub-hypergraphs in order
	to guarantee that $G_n$ is $r$-simple.
\end{proof}

@@

\begin{lemma}
	Let $X\subset \N$ be a finite set of fixed vertices, and let 
	$r\in \N$. Define $G_n^\prime=G_n \setminus E(X)$.
	Then (1) a.a.s $G^\prime_n$ does not contain a path of size
	$r+1$ between any two vertices $u,v\in X$, and (2)
	a.a.s $G^\prime_n$ does not contain a cycle containing
	any vertex $u\in X$.
\end{lemma}
\begin{proof}
	To prove the first part of the statement it suffices
	to show that the expected number of such paths
	tends to zero as $n$ tends to infinity. 
	Let $P$ be a path of size $r+1$ between two vertices $w,z$,
	and let $u,v$ be two vertices from $X$. 
	Given $f$ 	
\end{proof}

>>>>

The analyticity of these asymptotic probabilities with respect to 
the parameter $\beta$ implies that FO properties cannot "capture" sudden
changes that occur in the random graph $\mathrm{G}(n,\beta/n)$
as $\beta$ changes. Given $p(n)$ a probability, $P$ a property of graphs,
and $Q$ a sufficient condition for $P$ - i.e., a property that 
implies $P$ -, we say that $Q$ explains $P$ if $\mathrm{G}(n,p(n))$ satisfies 
the converse implication $P \implies Q$ asymptotically almost surely
(a.a.s.). A notable example of this phenomenon happens in the range 
$p(n)= \log(n)/n + \beta/n$ with $\beta$ constant. Erd\"os and R\`enyi
\cite{erdHos1960evolution} 
showed that for probabilities of this form $\mathrm{G}(n,p(n))$ 
a.a.s. is disconnected only if it contains an isolated vertex. 
An observation by Albert Atserias is the following:

@@

The main theorem of this section is the following
\begin{theorem} \label{thm:simple}
	Let $r\in \N$. Then a.a.s $G_n$ is $r$-simple. 
\end{theorem}

	The first moment method alone is not sufficient
	to prove our claim because the amount of dense 
	hypergraphs	$H$ such that $diam(H)\leq r$ is not finite
	in general. Thus, we need to prove that it suffices to
	prohibit a finite amount of dense sub-hypergraphs in order
	to guarantee that $G_n$ is $r$-simple.

@@

Now we are in conditions to prove \cref{thm:simple}.

@@

\begin{definition}

\end{definition}

\begin{lemma}
	Let $X\subset \N$ be a finite set of fixed vertices, and let 
	$r\in \N$. Define $G_n^\prime=G_n \setminus E(X)$.
	Then (1) a.a.s $G^\prime_n$ does not contain a path of size
	at most	$r+1$ between any two vertices $u,v\in X$, and (2)
	a.a.s $G^\prime_n$ does not contain a cycle of size $r+1$ 
	that contains a vertex $u\in X$.
\end{lemma}
\begin{proof}
	To prove the first part of the statement it suffices
	to show that the expected number of such paths
	tends to zero as $n$ tends to infinity. 
	Let $u,v$ be two vertices lying in $X$. 
	Given $f$ 	
\end{proof}
